---
title: "ESM 206 Fall 2021 Lab 8"
author: "Emily Pelstring, Chance English"
date: "11/16/2021"
output: html_document
---

## Set Up 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
library(janitor)
```

## Read in slo_homes.csv

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```

## Create a subset with 4 cities

task: create a subset called (homes_subset) that only contains observations where the city is: 

- "San Luis Obispo" 
- "Atascadero" 
- "Arroyo Grande" 
- "Santa Maria-Orcutt" 

```{r}
homes_subset <- homes %>%
  filter(City %in% c("San Luis Obispo",
                     "Atascadero",
                     "Arroyo Grande",
                     "Santa Maria-Orcutt"))
```

### A little exploration 

Task: create a summary table that has the mean and standard deviation of home prices grouped by city and sale status 

```{r}
homes_stats <- homes_subset %>%
  group_by(City, Status) %>%
  summarize(
    mean_price = mean(Price),
    sd_price = sd(Price),
    sample_size = n())
```

Task: Explore the relationship between square footage and home price (from homes_subset) in a scatterplot.

```{r}
ggplot(data = homes_subset, 
       aes( x = SqFt, y = Price)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

### Try a few linear models 

Use multiple linear regression to investigate relationships between several predictor variables and home Price using 'homes_subset'  

Create 2 different permutations of this model: 
(1) Price ~ City, Bedrooms, Bathrooms, SqFt, Status (lm1)
(2) Price ~ City, SqFt, Status (lm2)
(3) Try another one (Price ~ Bedrooms, Bathrooms) (lm3)

```{r}
lm1 <- lm(Price ~ City + Bedrooms + Bathrooms +SqFt + Status, data = homes_subset)

lm2 <- lm(Price ~ City + SqFt + Status, data = homes_subset)

lm3 <- lm(Price ~ Bedrooms, Bathrooms, data = homes_subset)

summary(lm1)

# If I wanted San Luis Obispo to be the reference level: 
# Use fct_relevel to specify a new reference level 

new_homes_subset <- homes_subset %>%
  mutate(City = fct_relevel(City, "San Luis Obispo"))

lm_slo <- lm(Price ~ City + SqFt, data = new_homes_subset)
summary(lm_slo)
```

What do these coefficients in `summary(lm1)` mean? 
If my houses are otherwise similar.. I would expect at home in San Luis Obispo to cost 13,904 dollars more than a house in Arroyo Grande. 
If my houses are otherwise similar... I would expect a home in Santa Maria-Orcutt to sell on average for 261,000 less than a similar home in Arroyo Grande. 

The R squared value means that 54% of variance in home price is explained by this model. 

### Explore correlations between quantitative variables 

Task: make a subset called homes_quant (from homes_subset) that only contains the variables from Price through SqFt)

```{r}
homes_quant <- homes_subset %>%
  select(Price:SqFt)

homes_cor <- cor(homes_quant)

corrplot(homes_cor)
```

### Compare AIC Values 

```{r}
AIC(lm1)
AIC(lm2)
```

Based on the AIC value, the trade off for model fit and complexity of the variables is not worth it; including the three variables is worth the added complexity according to the AIC values (the lower, the better)

### Use modelsummary() to return multiple model outputs 

```{r}
modelsummary(list(lm1, lm2, lm3))
```

### Check out diagnostic plots for lm1

```{r}
plot(lm1)
```

### use broom::augment() to return the predictions for existing observation 

```{r}
home_predictions <- augment(lm1)

# Make a histogram of the residuals from this model 
ggplot(data = home_predictions, 
       aes(x = .resid)) +
  geom_histogram()
```

